---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## CREDIT

The hard work was done by WSJ's Brian McGill ([@brian_mcgill](https://twitter.com/brian_mcgill/)) who **manually crafted** the base cartogram over **days** then translated that into the beautiful and illuminating creation that is the WSJ online delegate tracker: <https://www.wsj.com/graphics/elections/2020/track-the-delegate-count/>.

Brians's tweetnouncement: <https://twitter.com/brian_mcgill/status/1222556373864648704?ref_src=twsrc%5Etfw>

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(catchpole)

# current version
packageVersion("catchpole")

```

```{r u-1, fig.width=1300/96, fig.height=700/96}
library(sf)
library(catchpole) # hrbrmstr/catchpole
library(hrbrthemes)
library(tidyverse)

gg_catchpole() +
  theme_ft_rc(grid="") +
  theme(legend.position = "bottom")
```

## catchpole Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
